\chapter{Introduction}
With the development of future cities in mind, the interest in city networks has grown over the years. According to our client, a researcher of the built environment, cities do not function in isolation but are connected forming "systems of cities". However, appropriate information on how cities are connected and the strength of these connections is hard to find. An enormous amount of raw, unordered data is available to extract the relations from, however, there is no good way yet to process the data. According to Short et al. comparative statistics are not easily available and common assertions are repeated \cite{short1996dirty}. Similar assertions are made by DeRudder et al. \cite{derudder2005appraisal}. Using web data as a proxy for determining intercity relations is still unspoken of.
%However, it is still unknown what primarily causes economic growth. It could either be these benefits or an increase in the contesting position of the agglomeration in the global urban network. \\

The huge amount of textual data generated online and the numerous historic archives, such as Delpher\footnote{\url{http://www.delpher.nl}} and the British Newspaper Archive\footnote{\url{http://www.britishnewspaperarchive.co.uk/}}, are great sources of information on social and economic behaviours. The client's hypothesis is that "semantic association", the co-occurrence of cities within a single document, of cities can give insight in the connections between cities. These associations can be found using advanced text mining on newspapers and web pages. Similar to research efforts in other domains, such as financial trade \cite{preis2013quantifying} and sales forecasting \cite{wu2014future}, where socio-economic phenomenon are derived using web data, the client's wish is to develop an application that captures urban-urban interactions. An example of how one could try to achieve this using the Google search Engine\footnote{\url{https://www.google.com}} is \texttt{"Rotterdam Amsterdam" OR "Amsterdam Rotterdam"}, which searches for the co-occurrence of Amsterdam and Rotterdam. However, manually processing all results a search engine yields is not feasible, because one would have to read each page to determine which types of relationships the page contains. An application should process all the pages that contain co-occurrences of cities to determine what type of relations, for example transportation or leisure, between cities can be extracted from the document. Thus, we will answer the following question: 
how can a framework be designed for leveraging open data such that a metric for the strength of relationships between cities can be quantified and visualised?
%how can open data be leveraged such that a metric for the strength of relationships between cities can be defined and visualised? \\
%how can the strength of relationships between cities be extracted and visualised from open data using software? \\
%what approach is best suited for extracting and visualising the strength of relationships between cities through open data?
%what approach is best suited for extracting and visualising the global urban network from open data? \\

First, we discuss related work in chapter 2. Second, we explore the problem domain, identify the requirements for a solution to the problem and discuss issues that might arise in chapter 3. Third, we develop a methodology for a framework that satisfies the requirements and tackles the issues in chapter 4. In chapter 5, we explain how the framework was realised and discuss the the most important issues we were able to solve. Then, in chapter 6, we evaluate the product, showing how well it meets its requirements and review the development process. Next, we discuss open issues as well as some possible ethical issues that may come with the system. In chapter 8 we provide some recommendations for the system for future versions. We conclude in section 9.
