\chapter{Better Code Hub Guidelines}\label{bch_guidelines}
\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

Better Code Hub \cite{better_code_hub} checks our code according to ten guidelines:
\begin{enumerate}
    \item \textbf {Write short units of code} \\
    Units of code should be no longer than 15 lines.
    \item \textbf {Write simple units of code} \\
    Separate units of code should contain no more than 4 branch points (if, for, while, etc)
    \item \textbf{Write code once} \\
    Shared code should be extracted, either to a new unit or to a super class
    \item \textbf{Keep unit interfaces small} \\
    The number of parameters per unit of code should be no more than four.
    \item \textbf{Separate concerns in modules} \\
    Identify and extract responsibilities of large modules to separate modules and hide implementation details behind interfaces.
    \item \textbf{Couple architecture components loosely} \\
    minimizing the amount of interface code (e.g. by using 'abstract factory' design pattern)
    \item \textbf{Keep architecture components balanced} \\
    Organize code in such a way that the number of components is between 2 and 12, and ensure the components are of approximately equal size (keep component size uniformity less than 0.71).
    \item \textbf{Keep your codebase small} \\
    Refactor existing code to achieve the same functionality using less volume, and prefer libraries and frameworks over "homegrown" implementations of standard functionality.
    \item \textbf{Automate tests} \\
    Add tests for existing code every time you change it.
    \item \textbf{Write clean code}\\
    Remove useless comments, commented code blocks, and dead code. Refactor poorly handled exceptions, magic constants, and poorly named units or variables.  
\end{enumerate}